Binary companions of evolved stars in \apogee\ \DR: \\ Search method and catalog of $\sim$5,000 companions

### 2018-04-02 paper/1-catalog/twoface-catalog.tex
galex note

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}
\newcommand{\ncontrol}{16,384}
\newcommand{\lnKcut}{-0.2}
\newcommand{\nhighK}{4,898}
\newcommand{\nbimodal}{106}
\newcommand{\nunimodal}{322}

@@

Large spectroscopic surveys with repeat observations offer a novel way to study
binary star and companion populations.
Time-domain radial-velocity measurements of stars contain information about
massive companions: Even with two successive observations of a single star, a
difference in the measured radial velocities implies the existence of at least
one companion.
However, with few or imprecise radial-velocity measurements, the orbital
properties of the companion(s) may be poorly constrained (e.g.,
\citealt{Price-Whelan:2017}).
The vast majority of spectroscopic targets with repeat observations in the
largest (by number of objects) stellar spectroscopic surveys are observed just a
few times with sparse, non-uniform phase coverage.
Most prior searches for companions using survey RV data have therefore
restricted their searches to only sources with many, high-precision epochs, so
that the orbital solution can be unambiguously determined (e.g.,
\citealt{Troup:2016}), or have used simple statistics computed from the data to
study multiplicity (e.g., $\textrm{RV}_\textrm{max}$; \citealt{Badenes:2017}).

@@

Stars typically have companions.
Main sequence stars in the solar neighborhood more often appear in binary or
multiple star systems rather than as solitary stars (e.g.,
\citealt{Duquennoy:1991,Raghavan:2010,Tokovinin:2014,Moe:2017}).
This is likely a generic outcome of star formation, as, for example turbulent
fragmentation in collapsing protostellar clouds can produce stellar multiplets
within length-scales comparable to their spheres of influence (e.g.,
\citealt{Raskutti:2016}).
Binary and multiple star systems are therefore of great interest in
astrophysics: The population of stars and their companions encodes information
about star formation processes, stellar parameters and evolution, and the
dynamics of multi-body systems (for recent reviews, see
\citealt{Duchene:2013,Moe:2017}).

Most of what is known about stellar companions comes from studies of
nearby main-sequence (MS) stars.
Nearly 50\% of MS stars in the solar neighborhood have companions
(e.g., \citealt{Tokovinin:2014}).
MS stars with companions have a large dynamic range of constituent and orbital
characteristics.
For example, binary stars have mass-ratios that span from $\approx 0.03$
to 1 (e.g., \citealt{Kraus:2008}), and have periods from days to
millions of years (e.g., \citealt{Raghavan:2010}).
Less is known about population properties of non-interacting or detached
companions to evolved stars.

@@

@@

From this run, 91,096 stars completed and successfully returned \nposterior\
samples using \thejoker\ alone.
The remaining 5,135 stars did not return \nposterior\ samples: 4,744 were
flagged as \emph{needs more prior samples}, 391 as \emph{needs MCMC}.
We then proceed to generate \nposterior\ samples for these two subsets using the
methodology explained above (see \sectionname~\ref{sec:samplings}).
In the end, \todo{XX} stars have completed samplings with \nposterior\ samples,
and, after re-running \thejoker\ with twice as many prior samples, \todo{XX}
stars still have fewer samples that are multi-modal in period.

The full catalog of posterior samples for all \apogee\ stars in our parent
sample is available online.
\todo{Structure of table, where to download, make a webpage with some
information?}

@@

In \figurename~\ref{fig:mass}, a few interesting systems are immediately
obvious: From the left panel, two systems have bimodal period samplings in which
both period modes put the minimum companion mass below the Hydrogen-burning
limit (brown dwarf candidates), and two systems have $M_{2, \textrm{min}} > M_1$
(neutron star or black hole candidates).
In the right panel, one system appears right on the limit of being an
interacting binary ($q_{\textrm{min}} \approx 0.5$), but \todo{does it have
x-ray or UV data?}.
These systems are prime candidates for spectroscopic follow-up.

>>>>

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}
\newcommand{\ncontrol}{16,384}
\newcommand{\lnKcut}{-0.2}
\newcommand{\nhighK}{4,898}
\newcommand{\nbimodal}{106}
\newcommand{\nunimodal}{320}

@@

Time-domain radial-velocity measurements of stars contain information about
massive companions.
Even with two successive observations of a single star, a difference in the
measured radial velocities implies the existence of at least one companion.
However, with few or imprecise radial-velocity measurements, the orbital
properties of the companion(s) may be poorly constrained (e.g.,
\citealt{Price-Whelan:2017}).
The vast majority of spectroscopic targets with repeat observations in the
largest (by number of objects) stellar spectroscopic surveys are observed just a
few times with sparse, non-uniform phase coverage.
Most prior searches for companions using survey RV data have therefore
restricted their searches to only sources with many, high-precision epochs, so
that the orbital solution can be unambiguously determined (e.g.,
\citealt{Troup:2016}), or have used simple statistics computed from the data to
study multiplicity (e.g., $\textrm{RV}_\textrm{max}$; \citealt{Badenes:2017}).

@@

@@

Binary and multiple star systems are of great interest in astrophysics: The
population of stars and their companions encodes information about star
formation processes, stellar parameters and evolution, and the dynamics of
multi-body systems (for recent reviews, see \citealt{Duchene:2013,Moe:2017}).
Most of what is known about stellar companions comes from studies of nearby
main-sequence (MS) stars (e.g.,
\citealt{Duquennoy:1991,Raghavan:2010,Tokovinin:2014,Moe:2017}).
Nearly 50\% of MS stars in the solar neighborhood have companions
(e.g., \citealt{Tokovinin:2014}).
MS stars with companions have a large dynamic range of constituent and orbital
characteristics.
For example, binary stars have mass-ratios that span from $\approx 0.03$
to 1 (e.g., \citealt{Kraus:2008}), and have periods from days to
millions of years (e.g., \citealt{Raghavan:2010}).
Less is known about population properties of non-interacting or detached
companions to evolved stars.
The catalogs and methodology presented in this work are a first step towards
performing population inferences of binary star systems with evolved star
members.

@@

From this run, 91,096 stars completed and successfully returned \nposterior\
samples using \thejoker\ alone.
The remaining 5,135 stars did not return \nposterior\ samples: 4,744 were
flagged as \emph{needs more prior samples}, 391 as \emph{needs MCMC}.
We then proceed to generate \nposterior\ samples for these two subsets using the
methodology explained above (see \sectionname~\ref{sec:samplings}).
% In the end, \todo{XX} stars have completed samplings with \nposterior\ samples,
% and, after re-running \thejoker\ with twice as many prior samples, \todo{XX}
% stars still have fewer samples that are multi-modal in period.
The full catalog of posterior samples for all \apogee\ stars in our parent
sample is available online.
\todo{Structure of table, where to download, make a webpage with some
information?}

@@

In \figurename~\ref{fig:mass}, a few interesting systems are immediately
obvious: From the left panel, two systems have bimodal period samplings in which
both period modes put the minimum companion mass below the Hydrogen-burning
limit (brown dwarf candidates), and two systems have $M_{2, \textrm{min}} > M_1$
(neutron star or black hole candidates).
In the right panel, one system appears right on the limit of being an
interacting binary ($q_{\textrm{min}} \approx 0.5$), but has no significant UV
flux (\acronym{GALEX} DR5; \citealt{Bianchi:2011}).
These systems are prime candidates for spectroscopic follow-up.
